Abstract Data Type Inference

### 2015-03-16 algorithm.tex
formulas

\section{Computing Symbolic Representations}
\label{sec:algorithm}

@@

>>>>

%!TEX root = draft.tex
\section{Computing Symbolic Representations}
\label{sec:algorithm}

@@

Given a history $h = \tup{O,<,c,f,m}$, we define a formula $\textsc{Stronger}(h)$
describing all histories stronger than $h$ w.r.t. $\preceq$. The set of variables $X_O$
contains one variable $x_o$ for each $o\in O$.

\begin{align*}
\exists X_O. & \bigwedge_{o\in O} {\sf meth}(x_o)=f(o) \land \bigwedge_{o_1<o_2} x_{o_1} < x_{o_2}\land \bigwedge_{c(o)} {\sf c}(x_o) \\
& \land \bigwedge_{m(o_1)=o_2} {\sf match}(x_{o_1}) = x_{o_2} \\
& \land  \bigwedge_{o\in O} \forall x.\ {\sf match}(x) = x_o\Rightarrow \textsc{Dupl}(x,x_o)\vee {\sf rd}(x) 
\end{align*}

\begin{align*}
\textsc{Dupl}(x,x_o) \triangleq \bigvee_{o_1\in O} {\sf meth}(x_{o_1}) = {\sf meth}(x) \land {\sf match}(x_{o_1})=x_o
\end{align*}

For every two histories $h$ and $h'$,
\begin{align*}
h'\models \textsc{Stronger}(h) \mbox{ implies } h\preceq h'
\end{align*}

Let $Min(B)$ be the set of minimal elements of $B$. Then, the formula $F$ representing the ADT A is defined as:
\begin{align*}
F \triangleq \neg \bigvee_{h\in Min(B)} \textsc{Stronger}(h)
\end{align*}

  The formula $F$ represents $A$.
